Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-10-26 ms.tex
Updated author list.

\author{John H. Wise\altaffilmark{1,2}, 
  Tom Abel\altaffilmark{3}, 
  Ji-hoon Kim\altaffilmark{3}, 
  Peng Wang\altaffilmark{3,4},
  Peter Iannucci\altaffilmark{5}}

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\altaffiltext{4}{NVIDIA}
\altaffiltext{5}{Massachusetts Institute of Technology}
\email{jwise@astro.princeton.edu}

>>>>

\author{John H. Wise\altaffilmark{1}} 
\affil{Department of Astrophysical Sciences, Princeton University,
  Peyton Hall, Ivy Lane, Princeton, NJ 08544}

\author{Ji-hoon Kim and Tom Abel} 
\affil{Kavli Institute for Particle Astrophysics and Cosmology,
  Stanford University, Menlo Park, CA 94025}

\altaffiltext{1}{Hubble Fellow}
\email{jwise@astro.princeton.edu}
